---
title: "Code Splitting Obfuscation - An Empirical Assessment"
author: "PoliTo,FBK"
date: "2/6/2017"
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  html_document: default
graphics: yes
---
```{r setup,echo=FALSE}
#library(openxlsx)
library(plyr)
library(knitr)
library(ggplot2)
library(lmPerm)
library(grid)

#library(reshape2)
#library(likert)

load(file="CodeSplitData.R")

d$Correct <- d$Outcome == "SUCCESS"
d$Treatment <- factor(d$Treatment,c("C","TS","T"),ordered=TRUE)

# imputation!!!
d$Q1.TOT[is.na(d$Q1)] = d$Q2.TOT[is.na(d$Q1)]

d <- within(d,
{
  Q3.TOT<-Q3.SCORE/3
  C.SCORE <- (Q1.TOT + Q2.TOT + Q3.TOT)/3
})

strategy.levels = c(NA,"Internal","External","Both")
d$Strategy= factor(strategy.levels[1+d$Internal+d$External*2],strategy.levels,ordered=TRUE)


theme_set(theme_bw())
my.palette = c("#b2df8a","#1f78b4","#a6cee3")
my.palette = c("#e66101","#5e3c99","#b2df8a")


```


Results
=======

Descriptive statistics for the experiment 

```{r,echo=FALSE,results='asis'}
descriptive = ddply(d,.(Treatment),summarize,
                    n = length(Treatment),
                    Correct.n = sum(Correct) ,
                    Correct.p = sum(Correct) / length(Correct),
                    Time.mean = mean(Elapsed),
                    Time.sd = sd(Elapsed),
                    T.norm.p = shapiro.test(Elapsed)$p.value
                    )
kable(descriptive,digits = 2,
      col.names = c("Treatment","n","n Correct","prop Correct","Time mean","Time sd","T normality"),
      caption = "Summary statistics for Correctness and Elapsed Time .")
```


H1 Correctness
-----------

The proportion of correct completed tasks for the three treatments is reported in figure \ref{fig:PlotCorrectness}

```{r PlotCorrectness,echo=FALSE,fig.width=5,fig.height=3,warning=FALSE,out.width="0.9\\linewidth",fig.cap="Proportion of correctly completed tasks per Treatment.\\label{fig:PlotCorrectness}"}
cor.sum = ddply(d,.(Treatment),summarize,
                  Correct=sum(Correct)/length(Correct),
                  Correct.min = prop.test(sum(Correct),length(Correct))$conf.int[1],
                  Correct.max = prop.test(sum(Correct),length(Correct))$conf.int[2]
                )
p <- ggplot(cor.sum,
            aes(x=Treatment,y=Correct,color=Treatment,shape=Treatment))
#p <- p + geom_segment(aes(xend=C.SCORE,y=Correct.min,yend=Correct.max))
p <- p + geom_point(size=3.5,color="black")
p <- p + geom_point(size=3)
p <- p + ylab("Correctness")
p <- p + scale_color_manual(values=my.palette)
p <- p + scale_y_continuous(labels = scales::percent)
p
```

```{r HPc,echo=FALSE}
logit.mdl = glm(Correct ~ Treatment,data=d,family = "binomial")

kable(summary(logit.mdl)$coefficients,digits=3,
      caption="Logistic regression of Correctness vs. Treatment")
```

Both splitting treatmens (T and TS) have a significant effect on the correcteness of the attack task results.

Looking at the coefficients we observe that when the reference treatment is applied -- corresponding to the _(Intercept)_ coefficient -- we have a positive log-odds, i.e. the odds of a correct result vs. an incorrect one are larger than one.
While the coefficients of the two treatments are neagitive, meaning that they lower the odds of a correct result.


H2: Time
---------------

The distribution of elapsed time required to complete the task is reported in figure \ref{fig:PlotTime}.

```{r PlotTime,echo=FALSE,fig.width=5,fig.height=3,out.width="0.9\\linewidth",fig.cap="Boxplot of time to complete the task.\\label{fig:PlotTime}"}
p <- ggplot(subset(d,Correct),aes(x=Treatment,y=Elapsed,fill=Treatment))
p <- p + scale_fill_manual(values=my.palette)
p <- p + ylab("Elapsed Time [min]")
p <- p + geom_boxplot()
p
```


Linear regression ANOVA

```{r HP Time LR,echo=FALSE}

kwt = kruskal.test(Elapsed ~ Treatment,data=subset(d,Correct))

# 
# lmdl = lmp(Elapsed ~ Treatment,data=d#,
#            #contrasts = contrasts
#            )
# kable(summary(lmdl)$coefficients,digits=3,
#       caption="Anova of Time vs. Application and Treatment.")
# 
# 
# lmdl = lmp(Elapsed ~ Treatment, data=d,
#            list(Treatment = "contr.treatment")
#            )
# kable(summary(lmdl)$coefficients,digits=3,
#       caption="Anova of Time vs. Application and Treatment.")
```

The Kruskal-Wallis test result (p-value = `r kwt$p.value`) does not allow us to reject the null hypothesis: neither obuscation treatment has a significant effect on the attack task time.

## Co-factors


There three different tests for measuring the C knowledge skill.
The cross correlation of the three tests results are shown in the table below:

```{r , echo=FALSE}
#pairs(d[c("Q1.TOT","Q2.TOT","Q3.TOT")],col=(as.numeric(d$Correct)+1)*2)

kable(cor(d[c("Q1.TOT","Q2.TOT","Q3.TOT")]),digits = 2,
      caption="Cross correlation of the C knowledge tests")

```


Since they all the coefficients are relatively small, we decided to linearly combine the three tests outcomes to build a unique C knowledge score.

In addition we looked into the test 1 alone (just because we like fishing...).


### Correctness and C Skill

The effect of the C knowledge co-factor is reported in figure \ref{fig:PlotCorrCscore} for both test 1 alone and the combined score.

```{r PlotCorrCscore,echo=FALSE,fig.width=6,fig.height=6,out.width="0.9\\linewidth",fig.cap="Proportion of correctly completed tasks by Treatment and C Score.\\label{fig:PlotCorrCscore}"}

grid.newpage()
pushViewport(viewport(layout = grid.layout(2, 1)))


p <- ggplot(d,
            aes(y=Q1.TOT,x=Correct,fill=Treatment))
p <- p + geom_boxplot()
#p <- p + geom_line(aes(group=Treatment))
p <- p + xlab("Correct")
p <- p + ylab("C Knowledge Score (test 1)")
p <- p + scale_color_manual(values=my.palette)
p <- p + facet_grid(.~Treatment)
#p <- p + scale_y_continuous(labels = scales::percent)
#p

print(p,vp=viewport(layout.pos.row=1,layout.pos.col=1))

p <- ggplot(d,
            aes(y=C.SCORE,x=Correct,fill=Treatment))
p <- p + geom_boxplot()
#p <- p + geom_line(aes(group=Treatment))
p <- p + xlab("Correct")
p <- p + ylab("C Knowledge Score (combined score)")
p <- p + scale_color_manual(values=my.palette)
p <- p + facet_grid(.~Treatment)
#p <- p + scale_y_continuous(labels = scales::percent)
#p

print(p,vp=viewport(layout.pos.row=2,layout.pos.col=1))

```

The effect of the C knowledge, represented by the test 1 is reported in the following table:

```{r HPcC1,echo=FALSE}
logit.mdl = glm(Correct ~ Treatment + Q1.TOT,data=d,family = "binomial")

# d$C.LEVEL = d$C.SCORE/3
# logit.mdl = lmp(Correct ~ Treatment * C.LEVEL,data=d)

kable(summary(logit.mdl)$coefficients,digits=3,
      caption="Logistic regression of Correctness vs. Treatment and C Test 1")
```


The effect of the C knowledge, represented by the combined score is reported in the following tables:

```{r HPcCK,echo=FALSE}
logit.mdl = glm(Correct ~ Treatment + C.SCORE,data=d,family = "binomial")

# d$C.LEVEL = d$C.SCORE/3
# logit.mdl = lmp(Correct ~ Treatment * C.LEVEL,data=d)

kable(summary(logit.mdl)$coefficients,digits=3,
      caption="Logistic regression of Correctness vs. Treatment and Combined Score")
```

We observe no significant effect of the combine C knwoledge score on the correctness.


### Time and C Skill

The relationship between the elapsed time and the C skill (both test 1 and combined score) is reported in figure \ref{plotSTimeC}.

```{r plotScatterTimeC,echo=FALSE,fig.width=7,fig.height=7,out.width="0.9\\linewidth",fig.cap="Boxplot of time to complete the task vs. Treatment and C skill. \\label{plotSTimeC}"}

grid.newpage()
pushViewport(viewport(layout = grid.layout(2, 1)))

p <- ggplot(subset(d,Correct),aes(x=C.SCORE,y=Elapsed,color=Treatment))
p <- p + scale_fill_manual(values=my.palette)
p <- p + ylab("Elapsed Time [min]")
p <- p + xlab("Combined C Knowledge Score")
p <- p + facet_grid(.~Treatment)
p <- p + geom_point()
p <- p + geom_smooth(method="lm")
#p

print(p,vp=viewport(layout.pos.row=1,layout.pos.col=1))

p <- ggplot(subset(d,Correct),aes(x=Q1.TOT,y=Elapsed,color=Treatment))
p <- p + scale_fill_manual(values=my.palette)
p <- p + ylab("Elapsed Time [min]")
p <- p + xlab("Test 1 C Knowledge")
p <- p + facet_grid(.~Treatment)
p <- p + geom_point()
p <- p + geom_smooth(method="lm")
#p

print(p,vp=viewport(layout.pos.row=2,layout.pos.col=1))

```

The permutation test anova for C knowledge test 1 is reported in the following table:

```{r HPtC1,echo=FALSE}
lin.mdl = lmp(Elapsed ~ Treatment + Q1.TOT,data=subset(d,Correct),family = "binomial",settings=FALSE)

kable(summary(lin.mdl)$coefficients,digits=3,
      caption="Logistic regression of Elapsed Time vs. Treatment and C Test 1")
```

The test 1 C knowledge has a significant effect on the elapsed time.
With test 1 we achieve an $R^2$ =`r summary(lin.mdl)$adj.r.squared`.


```{r HPtCK,echo=FALSE}
lin.mdl = lmp(Elapsed ~ Treatment + C.SCORE,data=subset(d,Correct),family = "binomial",settings=FALSE)

# d$C.LEVEL = d$C.SCORE/3
# logit.mdl = lmp(Correct ~ Treatment * C.LEVEL,data=d)

kable(summary(lin.mdl)$coefficients,digits=3,
      caption="Logistic regression of Elapsed Time vs. Treatment and Combined Score")
```

The combined score for C knowledge has a significant effect on the elapsed time.

With the combined score we achieve an $R^2$ = `r summary(lin.mdl)$adj.r.squared`.


Type of attack
--------------

We identified two distinct categories of attack:

- internal: the computation inside specific functions has been altered,
- external: the actual parameter in function calls have been changed.

It is important to emphasize that during the attack task, both type could have been applied to achieve the goal.

Depending on the type of treatment one approach was easier to apply.

We can observe the number and percentage of participants that applied the two attach types in the following table.

```{r descriptive type of attack,echo=FALSE}
kable(
ddply(d,.(Treatment),summarize,
          n = length(Treatment),
          internal = sum(Internal==1),
          internal.pct = round(internal/n*100,1),
          external = sum(External==1),
          external.pct = round(external/n*100,1),
          both = sum(Internal==1 & External==1),
          both.pct = round(both/n*100,1)
      )
)
```

We observe that `r sum(d$Internal+d$External==0)` participants did not reported which strategy was applied!

We observe that clear code was much easier to attack with an internal approach,
the statistical significance of such a difference can be tested using a Fisher test comparing clear vs non-clear (either medium or small splitting).

```{r treatment vs. internal attack,echo=FALSE}
fisher.test(d$Treatment=="C",d$Internal)
```

The odds of an internal attack when a clear code is available are five times than for splitted code.


```{r treatment vs. external attack,echo=FALSE}
fisher.test(d$Treatment!="C",d$External)
```

Concerning the external attacks, the odds of adopting such an approach are 2.5 times highen when a splitted code is present. Though such a difference is not statistically significant in our experiments. Several participants, even with clear code, did apply such a strategy.


### Attack strategy vs. Success

```{r plotSuccStrategy, echo=FALSE,fig.width=8,fig.height=4, fig.cap="Success rate for different strategies by treatment"}
d.c = ddply(subset(d,!is.na(Strategy)),.(Treatment,Strategy),summarize,
      n = length(Treatment),
      Correct = sum(Correct)/length(Correct)
      )
d.c <- ddply(d.c,.(Treatment),transform,p = n/sum(n))

## vertical
# p <- ggplot(d.c,
#             aes(x=Strategy,y=Correct,color=Treatment,shape=Treatment))
# p <- p + facet_grid(.~Treatment)
# p <- p + geom_point(size=3.5,color="black")
# p <- p + geom_point(size=3)
# p <- p + ylab("Correctness")
# p <- p + scale_color_manual(values=my.palette)
# p <- p + scale_y_continuous(labels = scales::percent)

## horizontal
p <- ggplot(d.c,
            aes(y=Strategy,x=Correct,color=Treatment,shape=Treatment))
p <- p + facet_grid(Treatment~.)
p <- p + geom_point(size=3.5,color="black")
p <- p + geom_point(size=3)
p <- p + xlab("Correctness")
p <- p + guides(color=FALSE,shape=FALSE)
p <- p + scale_color_manual(values=my.palette)
p <- p + scale_x_continuous(labels = scales::percent)
#p <- p + geom_text(aes(x=.18,label=n),hjust=1,color="black")
p.dot = p


p <- ggplot(d.c,
            aes(x=Strategy,y=p,fill=Treatment))
p <- p + facet_grid(Treatment~.)
p <- p + geom_col(width=.5)
p <- p + ylab("Frequency of strategy") + xlab("")
p <- p + guides(fill=FALSE)
p <- p + scale_fill_manual(values=my.palette)
p <- p + scale_y_continuous(labels = scales::percent)
p <- p + coord_flip()
p.bar = p


grid.newpage()
pushViewport(viewport(layout = grid.layout(1, 2,widths=c(2,1))))
print(p.dot, vp = viewport(layout.pos.row = 1,layout.pos.col = 1))
print(p.bar, vp = viewport(layout.pos.row = 1,layout.pos.col = 2))

```


### Attack strategy vs. Time  

```{r plotSuccTime, echo=FALSE, fig.width=5, fig.height=3, fig.cap="Attack time for different strategies by treatment (successfull attacks only)"}
p <- ggplot(subset(d,Correct),aes(x=Strategy,y=Elapsed,fill=Treatment))
p <- p + facet_grid(Treatment~.)
p <- p + scale_fill_manual(values=my.palette)
p <- p + ylab("Elapsed Time [min]")
p <- p + geom_boxplot()
p <- p + coord_flip()
p
```


### Skill and strategy


```{r plotSkillStrategy, echo=FALSE, fig.width=5, fig.height=3, fig.cap="Skill of people adopting different strategies by treatment"}
p <- ggplot(subset(d,!is.na(Strategy)),aes(x=Strategy,y=C.SCORE,fill=Treatment))
p <- p + facet_grid(Treatment~.)
p <- p + scale_fill_manual(values=my.palette)
p <- p + ylab("C.SCORE")
p <- p + geom_boxplot()
p <- p + coord_flip()
p
```


